Array Programming with NumPy

### 2020-06-03 methods.tex
Edits to linalg paragraph

NumPy's linear algebra library provides an interface to established
linear algebra methods. These include solving linear systems of equations
and computing various matrix properties, such as the determinant,
the norm, the inverse, and the pseudo-inverse.
As well as computing the Cholesky, eigenvalue, and singular value decompositions
of a matrix and further functions.
For best performance and reliability the algorithms are provided by leveraging
an external implementation of the LAPACK interface \cite{LAPACK}.
LAPACK itself was first released in 1992 and is based on the EISPACK and LINPACK
open-source libraries. It is part of Netlib, a repository of
mathematical software, papers and databases and has a long history of open,
community-wide development \cite{dongarra1990lapack,dongarra2008netlib}.

>>>>

NumPy's linear algebra library includes functionality for: solving
linear systems of equations; calculating various matrix properties
such as the determinant, the norm, the inverse, the pseudo-inverse;
and computing the Cholesky, eigenvalue, and singular value
decompositions of a matrix.

The NumPy module mainly provides interfaces to established
implementations of the LAPACK (Linear Algebra PACKage) \cite{LAPACK}
interface.  LAPACK itself, which was first released in 1992, is, in
turn, based on the EISPACK and LINPACK open-source libraries. It is
part of Netlib, a repository of mathematical software, papers, and
databases, that has a long history of open, community-wide
development \cite{dongarra1990lapack,dongarra2008netlib}. For improved
performance, NumPy links to an accelerated BLAS (Basic Linear Algebra
Subprograms) implementation, most commonly OpenBLAS
(http://www.openblas.net/).
